Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
added motivation on the intro section

@@

\begin{itemize}
	\item The analysis of how security bugs evolve in time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item The relation of security bugs to the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We check if specific bugs are
eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
present how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}

>>>>

The motivation behind our work is to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we want to investigate other critical aspects associated with such
vulnerabilities. For instance, we want to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we want to check
if the relation between an artifact's size and its' software bugs applies 
to security bugs (citation needed). Finally, the structure of the Maven ecosystem,
gives us the oportunity to see if artifacts that is a dependency to a high
number of other artifacts contains a high rate of security bugs. In this case
we can strenghten the relationship between Linus' Law and software security as
Meneely et al. have already showed~\cite{MW10}.

@@

\begin{itemize}
	\item The analysis of how security bugs evolve in time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item We show evidence of the relation between security bugs and the artifact's size.  Here, size is
defined in terms of bytecode.
	\item Security bug persistense between versions. We show evidence that specific bugs are
not eliminated between versions.
	\item The correlation of security bugs with other bug categories. We
show evidence that such bugs are correlated with bugs that have to do with
performance, coding practices and others.
	\item The relation of software dependencies and security bugs. Our
hypothesis is that an artifact that is a dependency of many other artifacts
should have a low rate of security bugs. 
\end{itemize}
